\documentclass[paper=a4,fontsize=12pt]{scrartcl}
\fontfamily{SanSerif}						
\usepackage{graphicx}               
\usepackage[top=2cm]{geometry}


\frenchspacing              
\pagestyle{empty}          

\usepackage{sectsty}

\sectionfont{%			           	
	\sectionrule{0pt}{0pt}{-5pt}{3pt}}
		
\newcommand{\NewPart}[1]{\section*{\uppercase{#1}}}


\begin{document}

\NewPart{Projects}

\begin{enumerate}
	\item \textbf{AR Indoor Navigation}(Team project developed during Smart India \\ Hackathon) \textbf{5th - 6th March 2019}
    \begin{itemize}
    	\item The project aims at solving the problem of indoor navigation using Simultaneous Localization and Mapping
        \item An android application implemented in Unity, C\# and ARCore SDK.
	 \item Has an AR bot that guides you through the place (indoor).
        \item Uses Dijkstra's algorithm for finding the shortest path between the nodes that are dropped through our application.
    \end{itemize}
   \item \textbf{EduMR}(Team project) \textbf{September 2018}
	\begin{itemize}
	\item EduMR is an MR(Mixed Reality) base application for students to perform and explore in the playground provided (virtually) depending on the subjects.
\item An android application developed using Unity, C\# and Vuforia SDK.
\item Hardware requirements : VR Headset
	\end{itemize}
    \item \textbf{Certi-o-chan}(Team Project) \textbf{January 2019}
\begin{itemize}
\item Certi-o-chain aims to solve the problem of duplication of certificates using blockchain.
\item Our solution was an online service which would provide certificate on completeion of some course and then the pdf file would be converted into text and then stored in chains. At time of validation the pdf is again converted into text file and compared with the previous value sotred in chains.
\item Technology Stack: Python, HTML, CSS
\end{itemize}
    \item \textbf{E-Address Generator}(Team Project developed during Smart India \\ Hackathon 2017) \textbf{March 2018}
\begin{itemize}
\item EAddress is a digital solution to the traditional address mapping system. It
provides 12 digit Geospatial Embedded EAddress for all types of properties.
This E-address can be used instead of typing in the whole address
\item Techology Stack: HTML, CSS, JS, PHP
\end{itemize}

    \item \textbf{Data Analysis of Cryptocurrency}(Individual Project) \textbf{January 2018}
\begin{itemize}
\item Analysis on data of cryptocurrencies, plotting thier values of past 10 years and trying to predict the top 10 cryptocurrencies to invest in.
\item Techology Stack: Python, Libraries : Pandas, Numpy, Matplotlib
\end{itemize}

    \item \textbf{Pizza Customizer}(Individual Project) \textbf{September 2018}
\begin{itemize}
\item The site lets your customize your pizza by adding the toppings you love, and the bill is calculated depending on the toppings chosen.
\item Techology Stack: HTML, CSS, JS, Ajax
\end{itemize}
\end{enumerate}
\end{document}